Aplicação Lista de Compras \textit{Offline}\\em um Comércio Varejista de Pequeno Porte

### 2016-11-27 paper.tex
Corrected translations
Abstract more compreensive

\begin{abstract}
Even small companies that opt for some kind of system, many times just for legal obligations, don't realize the potential in automate processes. This article analyzes one this processes and develop, through the software development method, a mobile application accessible in most smartphones. This process is a simple shopping list, that beside solving some situations may be the starting point for some automations later. Because the printed list is used during the purchase, the offline access has been proposed and studied the existing technology for it.
\end{abstract}

>>>>

\begin{abstract}
Even small companies that opt for some kind of system, many times just for legal obligations, don't realize the potential in automate processes. This article analyzes one this processes and propose, through the software development method, a mobile application accessible in most smartphones. This process is a simple shopping list, that beside solving some situations perhaps come to be the starting point for some automations later. Because the printed list is used during the purchase, the offline access has been proposed and studied the existing technology for it.
\end{abstract}
